Turbulence in compact to giant H~II regions

### 2022-12-14 strucfunc_paper.tex
Finish Appendix A1

\section{Degradation of the structure function due to observational limitations}
\label{sec:degr-struct-funct}
Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.

To characterize the impact of the observational box size and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
We quantify how these observational limitations affect the determination of astrophysical interest parameters such as the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2 \). 
The artificial velocity maps are created using a modified version of the \textit{make$\_$extend} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K}.
The modification add a tapering to the power law so that the generated fields are uncorrelated at large scales.
The artificial fields follows a given power law with a correlation length giving a variance value indicated as true \(\sigma^2\).
Using this true \(\sigma^2\) we obtain the true \(r_0\) and these values are used as a reference in the experiments to quantify the variations.

@@

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-effect}
    \\[\bigskipamount]
    (b)\\
    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-fits}
  \end{tabular}
  \caption{
    Reduction of apparent velocity variance and correlation length
    due to finite box size.
    (a)~Empirical measurements of \(\sigma^2\) and \(r_0\).
    Colored dots show mean results from different simulated velocity fields,
    with different power law slopes.
    Colored shading shows the inter-quartile range over the different sub-images.
    The dashed line is an approximate analytic fit to these results
    (equation~\eqref{eq:ajustebox}).
    (b)~Determination of \(\sigma^2\) and \(r_0\) from fitting the model
    of equation~\eqref{eq:new-correlation-form}.
    Colored dots are mean results from different simulated velocity fields,
    while the dashed line is the same as in (a).
  }
  \label{fig:finite-box-effect}
\end{figure}

The Fig. \ref{fig:finite-box}a shows some of the artificial velocity fields used to study the variations in the structure function with respect to the size of the observational box.
Initially we have a velocity field of \(512 \times 512 \) pixels that is divided \(n\) times (with \(n = 1 - 6\)) producing \(N = 4^n\) fields , where each one has a linear size \(L \times L \) with \(L = 2^{9 -n}\).
The structure function is determined for each division and later we average all the divisions obtaining a characteristic structure function for \(L = 256, 128, 64,\) etc.

In the Fig. \ref{fig:finite-box}b we show in solid lines the normalized averaged structure functions for the maps in Figure \ref{fig:finite-box}a.
The number \(N\) of divisions and the length \(L\) are indicated for each structure function.
The shaded areas show the deviation that each averaged structure function has due to the different divisions. 
The horizontal and vertical blue dashed lines show the true \(r_{0}\) and the value of \(B(r) / \sigma^2 = 1 \), respectively.
The colored dotted lines indicate the averages, taking into account all the divisions of each map, of the apparent \(r_ {0}\) and the apparent \(\sigma^2 \).
It is clear that \(r_0\) and \(\sigma^ 2 \) decrease with respect to the true values as the size \(L\) of the observational box decreases. 
This analysis is performed on different maps (no images are shown) given a different power law in the velocity spectrum and different correlation lengths, giving the same results.

Fig. \ref{fig:finite-box-effect}a shows the empirical ratios of the correlation length of each averaged map with respect to the true correlation length (\(\text{apparent } r_ 0 /\text{true } r_0 \) ) and the ratio between the averaged variance of each divided map and the true variance (\(\text{apparent } \sigma^2  / \text{true } \sigma^2\)).
We observe that for the values where \(L> 20r_0 \) the change in the ratios is null.
It is for the values where \( L < 10 r_0 \) where there is a decrease.
This behavior is fulfilled for all simulated maps with different power law and correlation length in the velocity spectrum indicated with different colored circles in Figure \ref{fig:finite-box-effect}a.

On the other hand, Fig. \ref{fig:finite-box-effect}b shows the model-derived \(r_0\) and \(\sigma^ 2 \) values using the fitting procedure with the \texttt{lmfit} library.
In this case we see that the model fitting works much better than the empirical measurement, which gives reliable values so long \(L > 3r_0 \).

The empirical variations of the ratios is described by the  dashed line in Fig. \ref{fig:finite-box-effect} a and b, and is given by the equation:

\begin{equation}\label{eq:ajustebox}
\beta(r_0) = 1 - \exp \left[ \frac{L}{3.6r_0} \right] 
\end{equation}

>>>>

\section{Degradation of the structure function due to observational limitations}
\label{sec:degr-struct-funct}
% Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.

To characterize the impact of the finite map size
and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
We quantify how these observational limitations affect the determination of
the structure function parameters, such as
the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
The artificial velocity maps are created using a modified version of the \texttt{make\textunderscore{}extend} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
which creates a two-dimensional fractional Brownian Motion field
\citep{Miville-Deschenes:2003a}
based on a power-law energy spectrum in wavenumber \(k\) 
with random phases. 
Our modification multiplies the energy spectrum by a
low-wavenumber exponential taper:
\(e^{-1 / 2 \pi r_0 k}\).
As a result, the generated fields become uncorrelated at scales larger than \(r_0\)
and the resulting structure function closely approximates our model form
(section~\ref{sec:methods-apply}).

% The artificial fields follows a given power law with a correlation length giving a variance value indicated as true \(\sigma^2\).
% Using this true \(\sigma^2\) we obtain the true \(r_0\) and these values are used as a reference in the experiments to quantify the variations.

@@

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-effect}
    \\[\bigskipamount]
    (b)\\
    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-fits}
  \end{tabular}
  \caption{
    Reduction of apparent velocity variance and correlation length
    due to finite box size.
    (a)~Empirical measurements of \(\sigma^2\) and \(r_0\).
    Colored dots show mean results from different simulated velocity fields,
    with different power law slopes.
    Colored shading shows the inter-quartile range over the different sub-images.
    The dashed line is an approximate analytic fit to these results
    (\(1 - e^{L / 3.6r_0}\)).
    (b)~Determination of \(\sigma^2\) and \(r_0\) from fitting the model
    of equation~\eqref{eq:new-correlation-form}.
    Colored dots are mean results from different simulated velocity fields,
    while the dashed line is the same as in (a).
  }
  \label{fig:finite-box-effect}
\end{figure}

Figure~\ref{fig:finite-box}a shows how we test for finite map effects by taking
a simulated velocity field of size \(512 \times 512\) pixels and iteratively
dividing the full map into \(2 \times 2\) tiles.
On the \(j\)th iteration we have \(N = 4^j\) tiles,
each of size \(L \times L \) pixels with \(L = 2^{9 - j}\).
The figure shows the result for \(j = 1\), 2, 3, and 4, in which the full map
was generated with a correlation length \(r_0 = 16\)~pixels.
We then calculate the individual structure function for each tile and
find the mean and standard deviation for each level of subdivision,
showing the results in Figure~\ref{fig:finite-box}b.
It can be seen that the mean structure functions for each level
of subdivision (shown by colored dots and solid lines)
overlap very closely with one another, apart from deviations
due to edge effects when \(r > L/2\).
On the other hand, there is considerable dispersion between
individual tiles (shown by light colored shading) for the cases
where \(L < r_0\).

We next empirically measure the velocity variance and
apparent correlation length for each tile.
The velocity variance \(\sigma^2\) is found by
directly averaging over the pixels in the tile using equation~\eqref{eq:sig-pos},
while the apparent correlation length \(r_0\)
is found as the separation \(r\) for which \(B(r) = \sigma^2\),
using the tile's own empirically measured structure function and variance.
In Figure~\ref{fig:finite-box-effect}a we show how these
quantities deviate from the ``true'' values
(as measured on the full \(512 \times 512\) map)
as a function of the tile size \(L\).
It can be seen that the true values are successfully recovered
so long as the map size is more than ten times the correlation length,
but the apparent values of \(r_0\) and \(\sigma^2\) are smaller than the true values
when \(L < 10 r_0\), increasingly so as \(L\) becomes smaller.
This can be intuitively understood as due to the fact that a tile that
is small compared with the correlation length will
fail to sample the full range of velocity fluctuations,
leading to an underestimate of \(\sigma^2\).
Then the fact that \(B(r)\) increases with \(r\) in the power law regime
means there will be a concomitant underestimate of \(r_0\).

However, it is possible to do a considerably better job
of recovering the true \(\sigma^2\) and \(r_0\) by fitting our
heuristic model structure function of equation~\eqref{eq:model-strucfunc-ideal}.
This is shown in Figure~\ref{fig:finite-box-effect}b, where it can be seen
that the true parameters are reliably recovered so long as \(L > 3 r_0\),
which is a roughly \SI{0.5}{dex} improvement over the purely empirical method.
In order for the model fitting to work, the tile size must be large enough
that the structure function begins to show some flattening at the largest scales,
which is why the results are still inaccurate for the smallest values of \(L\)
that sample only the rising power-law portion of \(B(r)\).
